\Large \bf Vigor: Toward Carrier-Grade Software Network Functions

### 2016-10-26 doc/paper/paper.tex
Some corrections for the example section in the paper.

Alas, symbolic execution would never terminate. The reason is ``path explosion:'' there is a large (often infinite) number of paths to explore, so the SEE cannot finish.  Path explosion results from cyclomatic complexity~\cite{mccabe:cyclomatic}: every branch condition doubles the number of paths, and every loop multiplies it by a factor; in our case, three \code{if} conditions inside an infinite loop give rise to an infinite number of paths.

@@

Suppose we had an overapproximate model:
\begin{lstlisting}
void ring_pop_front(struct ring* r,
                    struct packet* p) {
  FILL_SYMBOLIC(p, sizeof(struct packet),
                "popped_packet");
}
\end{lstlisting}
Then the \code{ASSERT} would fail.

Now exhaustive SE of the code takes less than 100 millisec with our modified KLEE, regardless of the size of \code{CAP}.  The fact that the code does not crash on any path amounts to a proof of crash freedom. Or does it? The validity of the proof depends on (1)  our library implementation of \code{ring} not crashing; and (2) the symbolic model of \code{ring} accurately capturing how the \code{ring} implementation works.

@@

Here is the example of the proven specification for the function
\code{ring_pop_front}. We do not include the proof of this specification due to
space constraints:

@@

Vigor must also validate that the model used for SE matches the library spec. Some symbolic models work well for some code, while others work well for other code, so the Vigor library comes with {\em multiple} simple, overapproximating models for each component, and Vigor automatically chooses combinations of models for symbolically executing the NF code. Once it finds a combination of models with which the desired property (crash freedom, no memory leaks, absence of certain security vulnerabilities) can be proven, Vigor validates that the behaviors exposed by the model during verification are consistent with the component's formal specification.  Details on how it does this appear in \S\ref{sec:design}.

To validate the model fit for the particular use case, SEE dumps
all the call sequences (30 in this case) that may happen during the execution.
Vigor checks whether the symbolic model enumerated all the possible
outputs for each sequence.

@@

{\bf Step 3: Link the NF code with the verified library} of components. The resulting executable is guaranteed to be free of crashes, subject to the assumptions listed in~\S\ref{sec:limitations}.

>>>>

Alas, symbolic execution would never terminate. The reason is ``path explosion'': there is a large (often infinite) number of paths to explore, so the SEE cannot finish.  Path explosion results from cyclomatic complexity~\cite{mccabe:cyclomatic}: every branch condition doubles the number of paths, and every loop multiplies it by a factor; in our case, three \code{if} conditions inside an infinite loop give rise to an infinite number of paths.

@@

Now exhaustive SE of the code takes less than 100 millisec with our modified
KLEE, regardless of the size of \code{CAP}.  The fact that the code does not
crash on any path amounts to a proof of crash freedom. Or does it? The validity
of the proof depends on (1)  our library implementation of \code{ring} not
crashing; and (2) the symbolic model of \code{ring} accurately capturing how the
\code{ring} implementation works ({\em Step 3}).

Suppose we had an overapproximate model:
\begin{lstlisting}
void ring_pop_front(struct ring* r,
                    struct packet* p) {
  FILL_SYMBOLIC(p, sizeof(struct packet),
                "popped_packet");
}
\end{lstlisting}
Then the \code{ASSERT} from the previous listing would fail.

@@

Here is the example of the proven specification for the function
\code{ring_pop_front}. We do not include the certified implementation of this
specification due to space constraints:

@@

{\bf Step 3: Validate the model used for SE.}
The model must match the library spec. Some symbolic models work well for some code, while others work well for other code, so the Vigor library comes with {\em multiple} simple, overapproximating models for each component, and Vigor automatically chooses combinations of models for symbolically executing the NF code. Once it finds a combination of models with which the desired property (crash freedom, no memory leaks, absence of certain security vulnerabilities) can be proven, Vigor validates that the behaviors exposed by the model during verification are consistent with the component's formal specification.  Details on how it does this appear in \S\ref{sec:design}.

To validate the model fit for the particular use case, SEE dumps
all the call sequences (30 in this example) that may happen during the execution.
Vigor checks whether the symbolic model enumerated all the possible
outputs for each sequence.

@@

{\bf Step 4: Link the NF code with the verified library} of components. The resulting executable is guaranteed to be free of crashes, subject to the assumptions listed in~\S\ref{sec:limitations}.
